---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# read.so

[![Travis-CI Build Status](https://travis-ci.org/alistaire47/read.so.svg?branch=master)](https://travis-ci.org/alistaire47/read.so)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/alistaire47/read.so?branch=master&svg=true)](https://ci.appveyor.com/project/alistaire47/read.so)
[![Coverage Status](https://img.shields.io/codecov/c/github/alistaire47/read.so/master.svg)](https://codecov.io/github/alistaire47/read.so?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/read.so)](https://cran.r-project.org/package=read.so)

### Installation

read.so is not on CRAN, but you can install it with

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("alistaire47/read.so")
```


## Read Tables from Stack Overflow Questions into R

Sometimes you see a really interesting question on Stack Overflow, but the asker 
only presents the data as a presentation-style table instead of as runnable R 
code. Fear no more! read.so will read even heinous tables into a data frame 
in a trice.

### Read data frame print output back into R

For instance, should you want to return output copied from the R console back 
into your own session, use `read.so` for a data.frame, and `read_so` for a 
tibble. Pass in a filepath, a raw string of text, a vector of lines, or if the 
data is on the clipboard, nothing at all, and the functions will grab it for 
you:

```{r read.so}
library(read.so)

iris_lines <- capture.output(head(iris))

iris_lines

read.so(iris_lines)

read_so(iris_lines)

clipr::write_clip(head(iris))

read.so()
```

Further, `read_so` will attempt to read in the results of printing a tibble:

```{r read_so, message=FALSE}
mtcars_lines <- capture.output(readr::read_csv(readr::readr_example("mtcars.csv")))

mtcars_lines

read_so(mtcars_lines)
```

### Read Markdown tables into R

read.so can also read Markdown tables into R:

```{r read.md}
chick_lines <- capture.output(
    knitr::kable(head(ChickWeight), format = "markdown")
)

cat(chick_lines, sep = "\n")

read.md(chick_lines)

read_md(chick_lines)
```

It can handle a number of formats, including tables with delimiter rows 
composed of "-", "=", "+", and whitespace.
